Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-02 prop.tex
prop.tex Make sure it could be biult in Eclipse.
prop.tex Clean up the parts not related to the paper...

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
%% \ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

%%%%
\subsection{Proposed Activity I: Quantum States as Interactive Processes}

The early formalization of the process of computing using Turing
machines~\cite{Turing_1937,blum2012complexity} or the
$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a
computation as realizing a mathematical function. From our
perspective, the most important consequence of this view is that the
properties of the computed function existed independently of any
observation, calculation, or interaction. For example, a function is
\emph{injective} or not independent of any observation. An agent can
only interact with the computation by asking questions regarding its
input-output behavior and although such interaction would reveal
fragments of the computed function and its innate properties, it could
not change it or affect it in any way.

In a series of breakthrough papers that led to his Turing
Award~\cite{Milner:1993:EIT:151233.151240}, Milner argued that this
``closed system'' view of computation is too limiting as it cannot
adequately describe the increasingly pervasive \emph{interactive
  computations}. Milner explained that ``concurrency requires a new
conceptual framework'' and ``not merely an extension of the repertoire
of entities and constructions which explain sequential computing.'' In
his Turing Award lecture, he gives the following simple but compelling
example. Consider the following two programs:
\begin{verbatim}
Program P1: x := 1; x := x + 1 
Program P2: x := 2
\end{verbatim}
As closed systems, these two programs define the same relation, namely
the one that maps an input memory to an updated memory in which the
location named \verb|x| is assigned the value \verb|2|. An observer
with the ability of inquire about the value of \verb|x| at the end of
the computation cannot distinguish the two programs. But place the
programs in an environment which may involve interactions and the
equivalence is lost. Phrased in physical terms, we give the observer the
additional ability to access the location \verb|x| \emph{during} the
computation, not just to observe its final value. In computing terms,
we place each of the two programs \verb|P1| and \verb|P2| concurrently
with the program:
\begin{verbatim}
Program Q: x := 3
\end{verbatim}
In the combined system of \verb|P1| and \verb|Q| running concurrently,
the location \verb|x| may end up containing \verb|2|, \verb|3|, or
\verb|4|. But in the combined system of \verb|P2| and \verb|Q| running
concurrently, the location~\verb|x| can only end up containing
\verb|2| or \verb|3|. The lesson, phrased in physics terms, is that it
is not sensible to think of the properties of a system (like \verb|P1|
or \verb|P2|) independently of the observer (\verb|Q| in this
case). Indeed the observation \verb|x=4| cannot be said to have an
existence independently from the interaction between \verb|P1| and
\verb|Q|: it really emerges or is created as part of the observation
process and is not a pre-existing ``element of reality''.

This phenomenon is hardly a surprise to computer scientists or
physicists but embracing it fully does have far-reaching
consequences. In computer science, the big shift was to abandon the
idea that a computation has inherent internal meaning, e.g.,
representing a pure mathematical function. Instead \emph{the meaning
  of a computational process is its observable behavior.} In this
computational analogue to the theory of controlled open quantum
systems, it is not too difficult to imagine that, in the presence of
multiple interacting observers, the behavior observed by just one
agent would appear to involve hidden variables or action at a
distance. The well-established theory of observation of concurrent
processes and their equivalences~\cite{Hennessy1989} relies on
neither.

\paragraph*{Research Question.} Is it possible to adapt the theory of
observation of concurrent processes to the study of quantum states and
confirm that the observations exhibit the same Bell-like correlations?

\paragraph*{Research Question.} The theory of observation of
concurrent processes and the theory of measurement in quantum
mechanics are superficially different. Is it possible to reformulate
them in a common language to benefit each theory from insights derived
from the other theory?

\paragraph*{Research Question.} Does the computational and hence
\emph{testable} hypothesis that the quantum state is nothing but an
interactive system agree with the QBism perspective providing a
resolution to the same paradoxes (e.g., EPR~\cite{EPR1935} and Wigner's
friend~\cite{Wigner1961,Fuchs2010,Fuchs2012})?

%%%%%
\subsection{Proposed Activity II: Quantum Interval-valued Probability Measures}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

@@

%%%%%
\subsection{Proposed Activity III: Quantum Information Theorems}

@@

%%%%%
\subsection{Proposed Activity IV: Computational and Simulation Aspects}

The marriage of quantum mechanics and computer science first
envisioned and popularized by Feynman has created an awkward, but
opportune, moment. The embarrassing dilemma was concisely described by
Aaronson as follows~\cite{AaronsonArkhipov2011,BFRDARW2013}. 
Consider the following three statements:
\begin{enumerate}
\item[(A)] Textbook quantum mechanics is correct.
\item[(B)] There does not exist an efficient classical factoring
  algorithm.
\item[(C)] The extended Church-Turing thesis that probabilistic Turing
  machines can efficiently simulate any physically realizable model of
  computation is correct~\cite{BernsteinVazirani1997,Kaye2007}.
\end{enumerate}
There is overwhelming evidence to support each of these
statements. The theoretical framework of quantum mechanics (A) has
withstood decades of experimental confirmation. Entire industries are
founded on the assumption (B) that algorithms like RSA are secure and
they also have withstood years of attempted
attacks~\cite{boneh1999twenty,wiki:RSAFactoring}. Finally the
entire field of complexity theory in computer science which has also
withstood years of field testing rests, in essence, on assumption
(C)~\cite{Aaronson2005,Piccinini2015}. 
And yet one of these three statements \emph{must be false}! Indeed
if textbook quantum mechanics is false we concede (A). If it is
correct Shor's efficient factoring algorithm is realizable. If there
is a corresponding efficient classical factoring algorithm then we
concede (B). If not then we concede~(C).

It is unlikely that there will be a simple a resolution to this
awkward situation. It is more likely that the resolution will emerge
from deep and careful analyses of the foundations of each field. In
previous work, we examined the Hilbert space mathematical framework of
quantum mechanics and teased apart its various aspects that directly
rely on the infinite-precision real or complex numbers. We note two
remarkable earlier results and an open question:
\begin{itemize}
\item UNIQUE-SAT: Schumacher and
  Westmoreland~\cite{Schumacher2012-SCHMQT} argue that much of the
  structure of traditional quantum mechanics is maintained in the
  presence of finite fields. In particular, they establish that the
  quantum theory based on the finite field of booleans retains the
  following characteristics of quantum mechanics: the notions of
  superposition, interference, entanglement, and mixed states of
  quantum systems; the time evolution of quantum systems using
  invertible linear operators; the complementarity of incompatible
  observables; the exclusion of local hidden variable theories and the
  impossibility of cloning quantum states; and the presence of natural
  counterparts of quantum information protocols such as superdense
  coding and teleportation. However we have argued that this theory is
  not physically realizable as it allows the solution of
  computationally difficult problems like
  UNIQUE-SAT~\cite{Valiant198685} in constant time~\cite{usat}.

\item Deutsch-Jozsa: In a follow-up paper~\cite{DQT2014}, we proposed
  a variant of quantum mechanics in which the underlying field of
  complex numbers is replaced by special finite fields with enough
  structure to model Hermitian products that \emph{locally} behave
  like inner products. The trick is to recognize that, as the
  characteristic of the finite field increases, larger and larger
  regions of the finite field become totally ordered, thereby
  restoring, with some restrictions, all the usual properties of the
  inner product needed for conventional quantum mechanics. Using this
  theory to analyze the Deutsch-Jozsa algorithm reveals that the
  characteristic of the finite field plays an essential role: as the
  size of the finite field grows, so does the numerical range of the
  intermediate and final results of the algorithms being implemented.
  The theory naturally recovers a deterministic measure of the
  intrinsic resources required for a given level of complexity; this
  measure is normally completely hidden in computations with real
  numbers, and explicitly exposing it is one of the significant
  achievements of our discrete field analysis of quantum computation.
  This solves the conundrum that the conventional Deutsch-Jozsa
  algorithm~\cite{DeutschJozsa1992,Jaeger2007}
  mysteriously continues to work for larger and larger input
  functions without any apparent increase in resources.  Our analysis
  of this problem reveals that as the size of the input increases, it
  is necessary to increase the size of the finite field and hence the
  size of the underlying available numeric coefficients.  This
  observation does not fully explain the power of quantum computing
  over classical computing, but at least it explains that some of the
  power of quantum computing depends on increasingly larger precision
  in the underlying field of numbers.

\item An important special case of a generalized measurement is the
  symmetric, informationally complete, positive operator valued
  measure (SIC-POVM), which has applications in quantum
  cryptography. This problem has been formulated in the context of
  standard quantum theory where fields are complex numbers.  Although
  a rigorous proof for the existence of SIC-POVMs for arbitrary
  Hilbert space dimensions is still missing, it would be illuminating
  to look for a formulation of the same problem in a discrete quantum
  theory defined in terms of finite Galois fields.
\end{itemize}

A long term, ultimate, goal of this research proposal would be to
combine the various pieces into a coherent computational model of
quantum mechanics that keeps explicit track of resources needed to
represent the interactive system representing the quantum state, its
evolution, the observables, and the probabilities. Such a
computational model of quantum mechanics would encompass classical
(reversible) computation and potentially revolutionize quantum
thinking with finite resources. The explicit manipulation of resources
enables one of key idea that emerged in our previous work: the
resources used to represent the quantum system are in principle
unrelated to the resources available to the various observers. We
conjecture that this asymmetry may prove key to resolving some of the
quantum paradoxes.  The nature of quantum mechanics realized in terms
of discrete fields and finitely-communicable probability estimates is
amenable to direct computational exploration for reasonable field
sizes and observational accuracy. We have established a set of utility
libraries in Mathematica that supports a wide variety of such
numerical experiments. Concurrently to this effort, we are also
building on our previous work~\cite
{VDS2009,AGVS2005,VAS2006,finiteQC,Sabry:2003:MQC:871895.871900}
to build semantically well-founded implementations of the
computational models investigated in this proposal.

\paragraph*{Research Questions.} The aim of these implementations
include:
\begin{itemize}
\item Provide an experimental testbed to simulate physical phenomena
  (e.g.~\cite {OrtizEtAl2001,SommEtAl2002}) that complements the
  Mathematica libraries in which quantum algorithms can be simulated;
\item Establish connections between quantum programming concepts and
  classical programming concepts. We plan to make our software
  available for educational and research purposes; and 
\item Analyze the computational complexity of quantum theories and
  simulations based on discrete fields. What other (apart from
  UNIQUE-SAT) supernatural algorithms can be implemented in
  computational models based on discrete fields?
\item Determine, through numerical computations, solutions for
  SIC-POVM for small vector space dimensions.
\end{itemize}

% \begin{figure}
% \begin{center}
%   \includegraphics[scale=0.38]{HoughLineData.pdf}
% \end{center}
%   \caption{Curves of possible line parameters determined by noisy
%     data samples on a straight line in 2D space.}
% \label{houghline.fig}
% \end{figure}

% %%%%%
% \subsection{Proposed Activity V: Applications}

% A classic evidence-accumulation method known as the Hough
% transform~\cite{BallardGenHough1981}, which is very closely related to
% Bayesian evidence accumulation
% methods~\cite{CrandallEtal2005,CrandallEtal2006}, provides another
% example of how our proposal to define physical theories without exact
% real numbers could be combined with the measurement process. Simply
% described, the Hough transform as an abstraction of Bayesian schemes
% starts with a model of the theory being measured, typically a model
% that would ordinarily be treated {\it after\/} gathering the data by
% applying least squares to choose the optimal parameters.  But in this
% method, instead of thinking of, say, the model of a straight line
% $\hat{\mathbf{n}}\cdot \mathbf{x} = d$ as an equation for the points
% on a line $ \mathbf{x}_{i} = (x_{i},y_{i})$, we think of it as a
% time-accumulating {\it set\/} of equations for the distance $d$ of the
% nearest point on the line and the direction
% $ \hat{\mathbf{n}} = (\cos \theta, \sin \theta)$ from the origin to
% that point (the direction perpendicular to the line).  Thus each point
% of {\it evidence\/}, $(x_{i},y_{i})$, produces an {\it equation in the
%   parameter space\/} that is effectively a plot of all the possible
% values of $d(\theta)$ as a function of the possible angular directions
% $\theta$ pointing to the family of all possible lines.  A typical
% result from a set of errorful (it is impossible to measure real
% numbers, we recall) data measurements of points on a hypothetical
% straight line is shown in Fig.~\ref{houghline.fig}.

% The interesting step for us is now to realize that the {\it parameter
%   curves\/} shown in the figure do not need, or indeed, must not, be
% themselves infinitely precise real numbers, but they must themselves
% incorporate in some way a theory consistent with forbidding absolute
% precision.  In practice, then, the sinusoidal lines in Figure
% \ref{houghline.fig} all become fuzzy, and the accumulation of these
% fuzzy distributions produces peaks of likelihood around the values
% $(d_0, \theta_0)$ that are the optimal choices for the line describing
% the set of data.  Note that even {\it one\/} data point provides
% evidence on a set of hypotheses. The simple analysis we have outlined
% here is easily extended to much more complex situations in higher
% dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
% that essentially any physical theory that would ordinarily be
% described by a mathematical model using infinite precision numbers is
% potentially nonsensical from a computational point of view: computer
% scientists know perfectly well, and have been dealing with since the
% time of Turing and Shannon, that every single bit of precision in any
% number has a cost, and that there is not enough energy in the universe
% to compute even one general real number.  Thus the combination of
% physical models that, in some intrinsic fashion, contain only
% computable numbers, with theories of measurement and evidence in the
% fashion of the Hough transform example we have just presented, could
% contain the outline of entirely new ways of understanding what
% mathematical models of the physical world and its measurement actually
% could be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Broader Impact and Education}

\noindent (A) {\em Integration of research and education:} Courses on
advanced computational models and quantum information will be further
developed at Indiana University to communicate the basic concepts and
tools discussed in this proposal. Dr. Ortiz taught courses on
``Quantum information and Computation'' and Dr. Sabry has taught
courses on ``Quantum Computing'' for graduate students.  Dr.\ Hanson
has taught courses on scientific visualization and mathematical
modeling with emphasis on high-dimensional mathematics.  His numerous
Siggraph course presentations are embodied in his 2006 book {\it
  Visualizing Quaternions\/}~\cite{Hanson2006}, 
which remains the definitive treatment
of the subject for computer science and data analysis applications and
has sold thousands of copies. As a part of Dr.\ Hanson's commitment to
exposing and explaining the elements of higher mathematics to the
public, he has recently led the design of a free iPhone App, {\it
  4Dice\/}, that for the first time makes available an interactive
treatment of a correctly imaged simulation of the appearance of a
hypercube, realizing interactively his YouTube animation of the same
name.  This framework is now being generalized for a broad family of
iPhone Apps to permit the hands-on study of high-dimensional
mathematics.  These courses were highly appreciated by the students as
noted by their evaluations in making the material extremely accessible
and interesting.  The PIs plan to engage high school students or
undergraduates in the implementation of some of the ideas.  The PIs
have a long standing commitment to K-12 science and math education
(see also (C) below). The collaborative group efforts will provide
students, as well as the PIs with a unique learning experience. The
broadened perspectives gained through those efforts will contribute to
the PIs effectiveness as teachers and mentors. They also will enable
to better prepare students and postdocs for productive careers in an
increasingly competitive global economy. Students and postdocs are
encouraged to pursue collaborative research leading to a broader
scientific program. This is highlighted by the PIs students' close
contact with LANL, the Perimeter Institute, and the Institute for
Quantum Computing at Waterloo.

\medskip
\noindent (B) {\em Broadening the participation of underrepresented groups:}
Indiana University is engaged in attracting women and minorities in all
ranks. Several programs are aimed at specifically attracting outstanding
students into physics and computer science, and to expanding the pool of
candidates for fellowships. Targeted recruitment of minority graduate
students is facilitated by the Falicov Fellowship established in 2006. In
recent years, the School of Informatics and Computing has been fortunate to
hire several women and minorities for faculty positions, and we have been
working toward increasing the number of women and minorities among our
student population. To assist with this process, the PIs will encourage women
and minorities to apply for graduate positions as well as undergraduate
positions that may be made available by the grant and REU
supplements. Dr. Ortiz has minority students and Dr. Sabry has graduated a
female Ph.D. in 2005 and is currently assisting on the Ph.D. committees of
several others.

\medskip
\noindent (C) {\em Enhancing infrastructure and outreach:} Dr. Ortiz
has pursued broad outreach by giving talks on astronomy/astrophysics
in the local schools at Bloomington, Indiana, and by an interview in
the public radio on quantum information. Dr. Ortiz is also guiding a
high school student in work on interferometry in two and three slit
experiments. Dr. Ortiz also guides undergraduate research. All source
code produced by this project will be made freely available via the
web, and the results will be disseminated via technical reports,
conference papers, and journal articles.  The software and concepts we
have developed in the past have been employed by a wide variety of
commercial and noncommercial users.  Thus, we expect that the
successful completion of the proposed research will contribute to the
understanding of quantum and semi quantum computation. The educational
benefits that will flow from this proposal will extend beyond the
students of the participating research groups. The knowledge gained
through participation in the proposed research will further strengthen
the effectiveness of these outreach activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PI Team and Prior NSF Support}

\paragraph*{PI Team.} Over the past several years, the PIs, together
with other IU faculty members and students, have formed a group whose
main interest is the study of paradigms of computing that either arise
in nature or are inspired by natural phenomena. The PIs are especially
interested in how the laws of physics can inspire and guide our
abstract computational models, as well as exposing new insights into
the computational framework behind the natural world and the
computability of physical theory. Our group has been active in several
areas related to the theory behind quantum computation. Particular
areas include: mathematical foundations of quantum computation and
complexity~\cite{AGVS2005,VAS2006}, adiabatic quantum computing,
quantum logic, classical and quantum reversible programming
languages~\cite{Sabry:2003:MQC:871895.871900}, analog computation and
its limits, and optical computing. During the past several years, our
discussions have revolved around formulating variants of quantum
mechanics that are computable and that are as close to possible to
classical computing. Several preliminary results have emerged from our
collaboration~\cite{usat,finiteQC,geometry2013,DQT2014}, and the group
is very excited about the potential implications of those
results. This proposal brings forth a particular aspect of this
programme related to its applications to problem areas that have
traditionally been outside the conceptual framework of quantum
mechanics and programming language research. This proposal, if funded,
will give our group more recognition within the university which, at
this point, is committed to generously funding several ``emerging
areas of research''. With the establishment of a new Intelligent
Systems Engineering at Indiana University with a focus nanoscale
sensors and quantum engineering and the recent hires in Physics in
experimental atomic physics, ion-trap quantum simulation, computation,
and measurement, the PI group is in an excellent position to receive
additional funding from the University to reach a critical mass of
quantum information researchers.

\paragraph*{Prior Support.} There was no recent NSF support for
Dr. Ortiz. In the past five years, Dr. Sabry received one NSF grant
(award number 1217454) titled \emph{Information Effects} for the
amount of \$275,319.00 with start and end dates of 1 September 2012 --
31 August 2016.

\paragraph*{Intellectual Merit.} Computing is about processing
information. Physically speaking, information, like energy, is a
resource that obeys a conservation principle: information can never be
created nor destroyed; it is just transformed. Traditional models of
computation, however, have not embraced this conservation of
information as an explicit principle. Instead this principle appears,
after the fact, in applications such as information-flow security
which treats the amount of information released to the environment as
a possible security leak and such as differential privacy which
intentionally releases some random information to the user to confuse
potential attackers. This project has instead embraced the principle
of conservation of information as a key foundation for the design of
computational models. In one perspective, computation in these models
is constructed from reversible transformations that act on topological
spaces, deforming them, stretching them, and shrinking them but never
cutting nor glueing. The first main result of this project was the
design and implementation of a programming language which captures
these ideas and realizes them in the context of the new foundational
framework of Homotopy Type Theory. This framework combines ideas from
mathematics, logic, physics, and computation in a way that accounts
for a newly-recognized higher-dimensional structure of types. This
idea enabled us to not only represent programs as reversible
deformations but also to represent the reversible deformations
themselves as higher-level programs implementing reversible
optimizations of the underlying lower-level programs. In a second
breakthrough, viewing the higher-level programs as distinct proofs of
reversibility enabled the definition of types whose natural
cardinality is fractional. Having computations that manipulate
fractional types opens the door for a rich and novel class of
applications in which resource creation and resource use are
separated. This idea brings speedups and convenience in a way that is
similar to the speedup and convenience brought by the use of credit
cards to complete transactions without necessarily having the money at
hand: the monetary resource can be consumed by the merchant and only
later be reconciled by the buyer.

\paragraph*{Broader Impacts.} The idea of reversible computation and
its connection to quantum mechanics is at the heart of one of the
deepest mysteries in the universe. Any progress or theory that
explains physical principles computationally is likely to change our
worldview impacting everything from philosophy and religion to all
conventional sciences. The project resulted in the graduation of one
Ph.D. student with another one expected to graduate in Spring 2017,
the current supervision of two additional Ph.D. students, the
graduation of an MS student, and the hosting of a visiting scholar.

\paragraph*{Publications.} Several papers were published to report on
the results. On the foundational side, we have the following papers:
\begin{enumerate}
\item Computing with Semirings and Weak Rig Groupoids, ESOP, 2016
\item Superstructural Reversible Logic, Workshop on Linearity, 2014
\item Theseus: A High Level Language for Reversible
  Computing. Work-in-Progress report, RC 2014
\item Discrete Quantum Theories, J. Phys. A: Math. Theor. 2014.
\item Geometry of Discrete Quantum Computing, J. Phys. A:
  Math. Theor. 2013.
\item Isomorphic Interpreters from Logically Reversible Abstract
  Machines. RC 2012. 
\end{enumerate}
On the applications side, we have the following papers: 
\begin{enumerate}
\item Copredication in Homotopy Type Theory: A homotopical approach
  for formal semantics of natural languages. Workshop on Natural
  Language and Computer Science, 2016.
\item Contract Monitoring Semantics as Patterns of
  Communication. ICFP, 2015.
\item Extensible Effects: An Alternative to Monad
  Transformers. Haskell Symposium, 2013.
\item Encoding Secure Information Flow with Restricted Delegation and
  Revocation in Haskell. Workshop on Functional Programming Concepts
  in Domain-Specific Languages, 2013
\end{enumerate}
In addition to the publications, Dr. Sabry and collaborators maintain
a public repository with software related to the project. Dr. Sabry
was also invited to give talks at several venues, most notably:
\begin{itemize}
\item Colloquiumfest, University of Saskatchewan, Canada, 2014
\item Workshop on Quantum Information and Foundations of Quantum
  Mechanics, University of British Columbia, Vancouver, Canada, 2013
\end{itemize}

% (d) a listing of the publications resulting from the NSF award (a
% complete bibliographic citation for each publication must be provided
% either in this section or in the References Cited section of the
% proposal); if none, state "No publications were produced under this
% award."

% (e) evidence of research products and their availability, including,
% but not limited to: data, publications, samples, physical collections,
% software, and models, as described in any Data Management Plan; and

>>>>

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{proposal/prop.bib}
%% \ExecuteBibliographyOptions{sorting=nyt,maxbibnames=5,doi=false,isbn=false,url=false}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Activity II: Quantum Interval-valued Probability Measures}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{proposal/measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

@@

@@
